Scikit-learn: machine learning without learning the machinery

### 2014-07-01 article.tex
trim use of --

\paragraph{Project vision.}
%
Scikit-learn was born from the observation that most standard
machine-learning algorithms were out of reach of the users that could
most benefit from them: researchers --biologists, climate
scientists, experimental physicists-- or developers --for web
services or domain-specific applications.
%
Implementations mostly consisted of scattered pieces of code to download
on researchers' web pages, with the notable exception of
statistic-specific environments such as the R language \cite{Rmanual}, or
the Weka Java library \cite{hall2009weka}.

@@

In Fig.~\ref{fig:code} we give an example of fully functioning code to
do sentiment polarity classification for movie reviews: given a review,
it outputs whether the review is positive about the movie it concerns.
The code demonstrates the use of pipelines, and also shows how machine
learning ties into unrelated Python's modules: downloading, unpacking and
learning from a dataset are all done in one programming language.
This script first fetches a hand-labeled movie review dataset
\cite{pang2004} and unpacks it to disk using standard Python libraries.
It then loads these using scikit-learn data loading functions, makes a
pipeline of a \textsf{tf--idf} feature extractor
\cite{rennie2003tackling} --that turns strings into a sparse matrix based
on word frequencies-- and logistic regression, and finally trains the
model. Parameters for the feature extractor and the classifier
were set manually.

@@

The greatest asset of the scikit-learn project is its breadth of
contributors, coming from different backgrounds, working in different
institutions, with a variety of applications --more than 200 contributors
total, 15 active core contributors in the past year. Indeed, not only
is there strength in numbers, but also the convergence of points of views
make better code and better design. From a developer's perspective, the
project is managed with the goals of enabling newcomers to
contribute while keeping a high quality assurance. For these purposes, we
rely heavily on Github (\url{http://github.com}) with an online
development workflow relying on distributed version control using git,
and intensive code review. The code review process is a great asset to
raising the quality of the code, from all points of view: algorithmic,
numerical robustness, homogeneity of APIs, ease of use, documentation.
Another central aspect for quality in the project is the heavy use of
unit testing (up to 88\% of the lines of code are covered), run
continuously on all contributions thanks to the Travis platform
(\url{http://travis-ci.org}).

>>>>

\paragraph{Project vision.}
%
Scikit-learn was born from the observation that most standard
machine-learning algorithms were out of reach of the users that could
most benefit from them: researchers --biologists, climate
scientists, experimental physicists-- or developers of web
services or domain-specific applications.
%
Implementations mostly consisted of scattered pieces of code to download
on researchers' web pages, with the notable exception of
statistic-specific environments such as the R language \cite{Rmanual}, or
the Weka Java library \cite{hall2009weka}.

@@

In Fig.~\ref{fig:code} we give an example of fully functioning code to
do sentiment polarity classification for movie reviews: given a review,
it outputs whether the review is positive about the movie it concerns.
The code demonstrates the use of pipelines, and also shows how machine
learning ties into unrelated Python's modules: downloading, unpacking and
learning from a dataset are all done in one programming language.
This script first fetches a hand-labeled movie review dataset
\cite{pang2004} and unpacks it to disk using standard Python libraries.
It then loads these using scikit-learn data loading functions, makes a
pipeline of a \textsf{tf--idf} feature extractor
\cite{rennie2003tackling} (that turns strings into a sparse matrix based
on word frequencies) and logistic regression, and finally trains the
model. Parameters for the feature extractor and the classifier
were set manually.

@@

The greatest asset of the scikit-learn project is its breadth of
contributors, coming from different backgrounds, working in different
institutions, with a variety of applications: more than 200 contributors in
total, 15 active core contributors in the past year. Indeed, not only
is there strength in numbers, but also the convergence of points of views
make better code and better design. From a developer's perspective, the
project is managed with the goals of enabling newcomers to
contribute while keeping a high quality assurance. For these purposes, we
rely heavily on Github (\url{http://github.com}) with an online
development workflow relying on distributed version control using git,
and intensive code review. The code review process is a great asset to
raising the quality of the code, from all points of view: algorithmic,
numerical robustness, homogeneity of APIs, ease of use, documentation.
Another central aspect for quality in the project is the heavy use of
unit testing (up to 88\% of the lines of code are covered), run
continuously on all contributions thanks to the Travis platform
(\url{http://travis-ci.org}).
